Stochastic Approximation Monte Carlo with a Dynamic Update Factor

### 2019-11-08 papers/histogram/sad.tex
a bit more sloppy text about what we need to write regarding the LJ31 cluster

The heat capacity changes significantly even at these low temperatures
when the size of the cavity is increased.  We use a 2.5 cavity because
``everyone else'' does.

>>>>

The heat capacity changes significantly even at these low temperatures
when the size of the cavity is increased.  We use a 2.5 cavity because
``everyone else'' does.  For purposes of testing the convergence of
the algorithm, we don't need to solve for the true heat capacity.
Furthermore, the heat capacity at fixed volume is not the most
meaningful quantity to predict for a cluster.

Dependence on bin width.  Figure~\ref{fig:lj-cv-error} shows that the
heat capacity converges just as well for bin widths varying over two
orders of magnitude.  WL and $1/t$-WL show similar behavior, so this
is not new, but is encouraging.

Specifying temperature range rather than energy range is beneficial.
Both WL and $1/t$-WL are incredibly sensitive to the minimum energy
chosen, as seen in Fig.~\ref{fig:lj-cv-error}.  Cite previous work
that showed them not converging because it chose too low a minimum
energy, proving that it is \emph{not} a trivial procedure to determine
an appropriate energy range.  Specifying the temperature range
\emph{does} matter! We had to do a whole bunch of $1/t$-WL
computations in order to determine what would be a sufficient
low-energy cutoff.
